### 2016-10-19 IEEEtran/intro.tex
intro sentence for trentino consortia improved

The research is performed within the framework of the EU FP7 CIVIS project. It has test sites in Stockholm (Sweden) and Trento (Italy) with domestic energy consumers. 
% 
In Sweden, those who buy a home officially own the right to inhabit the estate and must join a corresponding \textit{housing cooperative} 
that owns and maintains its estates. The test site in Stockholm is composed of sixteen(?) housing cooperatives, each of which has annually elected board members who make energy related decisions on behalf of the cooperative members. 
In the case of Trento test site, two local \textit{electricity consortia} are managing energy related issues. The consortia are particularity  interested in load shifting since the Trento households also have PV panel productions.  
This two types of communities are at the center of YouPower design. 
% 
The rest of this paper presents the design process of YouPower, gives an overview of the platform, and discuss in more detail its design concept.

>>>>

The research is performed within the framework of the EU FP7 CIVIS project. It has test sites in Stockholm (Sweden) and Trento (Italy) with domestic energy consumers. 
% 
In Sweden, those who buy a home officially own the right to inhabit the estate and must join a corresponding \textit{housing cooperative} 
that owns and maintains its estates. The test site in Stockholm is composed of sixteen(?) housing cooperatives, each of which has annually elected board members who make energy related decisions on behalf of the cooperative members. 
In the case of Trento test site, two local \textit{electricity consortia} produce, distribute and sell electricity to their associate members, by relying on renewable energy sources (hydro and solar power). The consortia are particularity interested in load shifting to optimize the use of their locally produced energy and minimize dependency from the national grid. Furthermore, privately owned PV panels are particularly common for the households in these areas.  
This two types of communities are at the center of YouPower design. 
% 
The rest of this paper presents the design process of YouPower, gives an overview of the platform, and discuss in more detail its design concept.
